### 2015-07-09 2015-compmorphon-morphver/poster.tex
layout switch
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@61235 72bbbca6-d526-0410-a7d9-f06f51895060

		\headerbox{Example: Tuvan velar elision}{name=tuvanvelars,column=1,span=2}{
			\begin{multicols}{2}
				\htwo{Previous descriptions}

@@

		\headerbox{Example: Tuvan vowel harmony}{name=tuvanvowelharmony,column=3}{ %{name=otherexamples,column=1,span=2,below=tuvanvelars}{ % after consonant clusters in loanwords
			%\begin{multicols}{2}
				\htwo{Tuvan vowel harmony}
					\begin{itemize}
						\item High and low vowels harmonise in \hilitetwo{back}ness\\
						киж\hiliteone{и}\tag{n}\tag{pl}\tag{acc}: киж\hiliteone{и}л\hiliteone{е}рн\hiliteone{и}, н\hilitetwo{о}м\tag{n}\tag{pl}\tag{acc}: н\hilitetwo{о}мн\hilitetwo{а}рн\hilitetwo{ы}
						\item High vowels also harmonise in roundness\\
						round: \hiliteone{ө}г\tag{n}\tag{acc}:\ \hiliteone{ө}гн\hiliteone{ү}, \hilitetwo{о}й\tag{n}\tag{acc}:\ \hilitetwo{о}йн\hilitetwo{у}\\
						unround: ү\hiliteone{е}\tag{n}\tag{acc}:\ ү\hiliteone{е}н\hiliteone{и}, \hilitetwo{а}й\tag{n}\tag{acc}:\ \hilitetwo{а}йн\hilitetwo{ы}
					\end{itemize}
				\htwo{Initial implementation (high-vowels)}

@@

	\headerbox{Example: Categorisation}{name=adjectives,column=3,below=tuvanvowelharmony}{
		\htwo{Unrestricted 0-derivation}
		\begin{itemize}
			\item Common overgeneralisation of adjective morphology:
			\begin{itemize}
				\item all adjectives may act like nouns (i.e.\ take noun morphology)
				\item all adjectives may be used as is as adverbs
			\end{itemize}
			\item Commonly reported in Turkic language grammars
		\end{itemize}
		%Somfai Kara (2002, pp. 28-29):\ \includegraphics[width=0.53\textwidth]{img/kara28}\\
		\textcite[28-29]{somfaikara02}:\ \includegraphics[width=0.53\textwidth]{img/kara28}\\
		\-\hfill{}\includegraphics[width=0.8\textwidth]{img/kara29}

@@

		\headerbox{References}{name=references,column=1,below=tuvanvelars}{
			\vspace{-0.42em}
			\begin{spacing}{0.3}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.05em}
		}

@@

		\headerbox{Further information}{name=getting,column=2,below=adjectives,span=2}{
			%\vspace{-0.2em}
			\tikzoverlay[text width=0.8in] at (6.73in, 0.04in) {
				\includegraphics[height=0.8in]{qrcode}
			};
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} (\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}), \textbf{source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
		}

>>>>

		\headerbox{Example: Tuvan velar elision}{name=tuvanvelars,column=2,span=2}{
			\begin{multicols}{2}
				\htwo{Previous descriptions}

@@

		\headerbox{Example: Tuvan vowel harmony}{name=tuvanvowelharmony,column=1}{ %{name=otherexamples,column=1,span=2,below=tuvanvelars}{ % after consonant clusters in loanwords
			%\begin{multicols}{2}
				\htwo{Tuvan vowel harmony}
					\begin{itemize}
						\item High and low vowels harmonise in \hilitetwo{back}ness\\
						киж\hiliteone{и}\tag{n}\tag{pl}\tag{acc}: киж\hiliteone{и}л\hiliteone{е}рн\hiliteone{и}, н\hilitetwo{о}м\tag{n}\tag{pl}\tag{acc}: н\hilitetwo{о}мн\hilitetwo{а}рн\hilitetwo{ы}
						\item High vowels also harmonise in roundness\\
						round: \hiliteone{ө}г\tag{n}\tag{acc}:\ \hiliteone{ө}гн\hiliteone{ү}, \hilitetwo{о}й\tag{n}\tag{acc}:\ \hilitetwo{о}йн\hilitetwo{у}\\
						unround: ү\hiliteone{е}\tag{n}\tag{acc}:\ ү\hiliteone{е}н\hiliteone{и}, \hilitetwo{а}й\tag{n}\tag{acc}:\ \hilitetwo{а}йн\hilitetwo{ы}
					\end{itemize}
				\htwo{Initial implementation (high-vowels)}

@@

	\headerbox{Example: Categorisation}{name=adjectives,column=1,below=tuvanvowelharmony}{
		\htwo{Unrestricted 0-derivation}
		\begin{itemize}
			\item Common overgeneralisation of adjective morphology:
			\begin{itemize}
				\item all adjectives may act like nouns (i.e.\ take noun morphology)
				\item all adjectives may be used as is as adverbs
			\end{itemize}
			\item Commonly reported in Turkic language grammars
		\end{itemize}
		%Somfai Kara (2002, pp. 28-29):\ \includegraphics[width=0.53\textwidth]{img/kara28}\\
		\textcite[28-29]{somfaikara02}:\ \includegraphics[width=0.53\textwidth]{img/kara28}\\
		\-\hfill{}\includegraphics[width=0.8\textwidth]{img/kara29}

@@

		\headerbox{References}{name=references,column=3,below=tuvanvelars}{
			\vspace{-0.42em}
			\begin{spacing}{0.3}
				\printbibliography[heading=none]
			\end{spacing}
			\vspace{-0.05em}
		}

@@

		\headerbox{Further information}{name=getting,column=1,below=adjectives,span=2}{
			%\vspace{-0.2em}
			\tikzoverlay[text width=0.8in] at (6.73in, 0.04in) {
				\includegraphics[height=0.8in]{qrcode}
			};
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} (\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}), \textbf{source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
		}
